---
title: "Untitled"
author: "DAVID DE VEGA MARTIN"
date: "13/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

https://www.displayr.com/sankey-diagrams-r/

https://rdrr.io/cran/PantaRhei/src/inst/doc/panta-rhei.R  <---- PROBAR
https://cran.r-project.org/web/packages/PantaRhei/vignettes/panta-rhei.html

https://plotly.com/r/sankey-diagram/

```{r}
library(networkD3)  # <-------------- libreria SANKY PLOT
library(htmlwidgets)
library(htmltools)
```


```{r}
nodes = data.frame("name" = 
 
  c( "Poblacion: 47.394.223",# Node 0
   "Pob >= 16 años: 39.694.300",# Node 1
   "Pob < 16 años: 7.699.923",# Node 2
   "", # Node 3
   "Pob. Activos: 23.447.700",  # Node 4
   "Pob Inactivos: 16.201.600",  # Node 5
   "Ocupados: 20.031.000",  # Node 6
   "Sector Privado: 16.547.000",  # Node 7
   "Sector Publico: 3.484.000", # Node 8
   "Parados: 3.416.700", # Node 9
   "Pensionista: 10.309.270", # Node 10
   "Ingreso minimo vital: 316.000", #Node 11
   "Inact Otros: 5.576.330" #Node 12
    ))

links = as.data.frame(matrix(c(
 
  #nodo_origen,nodo_final,cantidad
  
  0,1,47394223, # total
  1,2,7699923, # <16 años
  1,3,39694300, # >16 años
  3,4,23447700, # activos
  3,5,16201600, # inactivos
  4,6,20031000, # ocupados
  6,7,16547000, # s.privado
  6,8,3484000, #s.publicos
  4,9,3416700, # parados
  5,10,10309270, # pensionista
  5,12,5576330, # otros inactivos
  5,11,316000 # imv0
  ), byrow = TRUE, ncol = 3))



names(links) = c("source", "target", "value")


sankey <- sankeyNetwork( Links = links, Nodes = nodes,
          Source = "source", Target = "target",
          Value = "value", NodeID = "name" , 
          fontSize= 12, nodeWidth = 5,nodePadding = 30,
          colourScale = JS("d3.scaleOrdinal(d3.schemeCategory10);"
          ))

```


```{r}
sankey
```



```{r}
nodes1 = data.frame("name" = 
 
  c( "Poblacion",# Node 0
   "Pob >= 16 años",# Node 1
   "Pob < 16 años",# Node 2
   "", # Node 3
   "Pob. Activos",  # Node 4
   "Pob Inactivos",  # Node 5
   "Ocupados",  # Node 6
   "Sector Privado",  # Node 7
   "Sector Publico", # Node 8
   "Parados", # Node 9
   "Pensionista", # Node 10
   "Ingreso minimo vital", #Node 11
   "Inact Otros" #Node 12
    ))

links = as.data.frame(matrix(c(
 
  #nodo_origen,nodo_final,cantidad
  0,1,47394223, # total
  1,2,7699923, # <16 años
  1,3,39694300, # >16 años
  3,4,23447700, # activos
  3,5,16201600, # inactivos
  4,6,20031000, # ocupados
  6,7,16547000, # s.privado
  6,8,3484000, #s.publicos
  4,9,3416700, # parados
  5,10,10309270, # pensionista
  5,12,5576330, # otros inactivos
  5,11,316000 # imv0
  ), byrow = TRUE, ncol = 3))

names(links) = c("source", "target", "value")


sankey1 <- sankeyNetwork( Links = links, Nodes = nodes1,
          Source = "source", Target = "target",
          Value = "value", NodeID = "name" , 
          fontSize= 18, nodeWidth = 5,nodePadding = 30,
          colourScale = JS("d3.scaleOrdinal(d3.schemeCategory10);"
          ))

# sankey <- htmlwidgets::prependContent(sankey, htmltools::tags$h1("Title"))
# sankey <- htmlwidgets::appendContent(sankey, htmltools::tags$p("Caption"))
```


```{r}
sankey1
```


